---
title: "Advanced ttest"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Advanced ttest}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(ttest)
```

# Introduction
Run a t-test from two vectors.

# myttest()
Run a t-test based off of two vectors

## Input
x - An x vector of numeric values

y - A y vector of numeric values

alpha - An error rate value that is numeric

paired - A TRUE/FALSE value stating if the vector inputs are independent
    Default: TRUE

## List output
Data - a data frame of x and y

CI - the confidence interval of the test

type - test type ("paired", "t-test" (equal variance), "Welch" (unequal variance))

nullAccept - Y/N answer to "Do we accept the null hypothesis?"

x - x vector

y - y vector


# Print method
print.Rttest method used to print objects from myttest() of class "Rttest".

## Input
funObject - object equal to valid myttest()

## Output
A kable version of the data set made from the input vectors x and y.

The confidence interval from the selected t-test.

(Requires `kableExtra`)

# Plot method
plot.Rttest method used to plot objects from myttest() of class "Rttest".

Blue plot - base R

Green plot - ggplot2

## Input
funObject - object equal to valid myttest()

### NOT REQUIRED
i, j - x and y vectors from object index

k - test type: "paired", "t-test" (equal variance), "Welch" (unequal variance)

** NOT ADVISED TO CHANGE

## Output
Dot plots of x and y stating what type of test was used in the title

# Example

`myttest(x=rnorm(30,5,2), y=rnorm(30,3,2), alpha=0.05)`
